Comprehensive quality - aware Automated Semantic Web Service Composition

### 2016-11-02 paper.tex
update

\begin{algorithm}[!htb]
 \setlength\hsize{0.9\linewidth}
 \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
 \SetKwFunction{connectNode}{connectNode}\SetKwFunction{findCands}{findCands}\SetKwFunction{removeDangling}{removeDangling}
 \LinesNumbered
 \SetNlSty{}{}{:}
 \Input{$I$, $O$, $queue$}
 \Output{composition weighted graph $WG$}
 Create $start$ vertex with outputs $I$ and $end$ vertex with inputs $O$\;
 Create graph $WG$ containing the $start$ vertex\;
 Create available outputs set containing $start$ outputs\;
 \While{available outputs do not satisfy $end$ inputs}{
 Get next candidate from queue\;
 \If{candidate inputs are satisfied by available outputs}{
 \textcolor{blue}{Create edge assigned with weight\;}
 \textcolor{blue}{Connect vertex to graph with the edge\;}
 Remove it from queue and go back to the queue's beginning\;
 }}
 Connect end vetex\;
 Remove dangling vertices from graph $WG$\;
 Remove dangling edges from graph $WG$
 \KwRet $WG$\;
 \caption{Create a composition weighted graph from a queue}
\label{graph_building}
\end{algorithm}

>>>>

\begin{algorithm}[!htb]
 \setlength\hsize{0.9\linewidth}
 \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
 \let\oldnl\nl% Store \nl in \oldnl
\newcommand{\nonl}{\renewcommand{\nl}{\let\nl\oldnl}}
 \Input{$I$, $O$, $queue$}
 \Output{composition weighted graph $WG$}
 \textbf{1.} Create $start$ vertex with outputs $O$ and $end$ vertex with inputs $I$.\\
 \textbf{2.} Create graph $WG$ containing the $start$ vertex.\\
 \textbf{3.} Create available outputs set containing $start$ outputs.\\
 \While{available outputs do not satisfy $end$ inputs}{
 \textbf{4.} Get next candidate from queue.\\
 \If{candidate inputs are satisfied by available outputs}{
 \textcolor{blue}{\textbf{5.} Create edge assigned with weight.\\}
 \textcolor{blue}{\textbf{6.} Connect vertex to graph with the edge.\\}
 \textbf{7.} Remove it from queue and go back to the queue's beginning.\\
 }}
 \textbf{8.} Connect end vertex.\\
 \textbf{9.} Remove dangling vertices from graph $WG$.\\
 \textcolor{blue}{\textbf{10.} Remove dangling edges from graph $WG$.\\}
 \KwRet $WG$.\\
 \caption{Create a composition weighted graph from a queue}	
\label{graph_building}
\end{algorithm}
